Software Citation Principles

### 2016-03-22 sc-principles/software-citation-principles.tex
utf-8 encoding

In astronomy \& astrophysics: ASCL \cite{ascl}, AAS journals  and the joint
AAS/GitHub workshop \cite{aas-software-index} dedicated to software citation,
indexing and discoverability.

>>>>

In astronomy \& astrophysics: ASCL \cite{ascl}, AAS journals  and the joint
AAS/GitHub workshop \cite{aas-software-index} dedicated to software citation,
indexing and discoverability, and the report from a Birds of a Feather session
organized by the ASCL at the Astronomical Data Analysis Software and Systems
(ADASS) XXV conference \cite{2015arXiv151207919A}.
